---
title: "Simple document"
author: AJ Catalano
date: 28 October 2021
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

Code below creates a data frame and generates a plot.

"eval = FALSE" shows code without running it
"echo = FALSE" runs code without showing the code
"message = FALSE" shows only output
"include = FALSE" acts as if code did not exist
"collapse = TRUE" collapses all output into one place not separated by code chunks

# Section 3

#### Plots

```{r plot_example}
# comment for code chunk
library(tidyverse)

plot_df = tibble(
  x = rnorm(500, mean = 2, sd = 4),
  y = 3 - 4.2 * x + rnorm(500)
)

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```
This plot is neat. It shows a linear relationship.

The data frame has `r nrow(plot_df)` rows.

# Section 4

#### Making lists

Here is a list of things I like:

* Techno
* Synthesizers
  * Analog
  * Digital
  * Modular
* Drum machines

#### Table construction

Col 1 | Col 2
----- | -----
  a   |   b
  c   |   d
  e   |   f